Named Entity Recognition for Web Data Extraction

### 2019-05-20 tex/article.tex
Artigo NLE.

% \author[João Mateus de Freitas Veneroso and Berthier Ribeiro-Neto]
%        {João Mateus de Freitas Veneroso$^A$ \and
%         Berthier Ribeiro-Neto$^B$\\
% 	Universidade Federal de Minas Gerais$^{A,B}$ \\
% 	Google Engineering$^A$, Belo Horizonte - MG, Brazil}

@@

Some early examples are Maximum Entropy Taggers for NER~\cite{Borthwick1998} and
\gls{pos} Tagging~\cite{Ratnaparkhi1998}. The Maximum Entropy Markov Model~\cite{McCallum2000} 
was developed just a while later, building up on the intuition of \gls{hmm}s combined with
the flexibility of discriminative approaches. However, because of the label bias problem,
this model was superseded by \gls{crf}s~\cite{Lafferty2001, McCallum2003}. 
At this time, the best performing systems almost always resorted to external gazetteers 
and hand-chosen features, as is the case for the {CoNLL-2003} winning model~\cite{Florian2003}.

@@

Many \gls{wde} systems rely on hand crafted rules or gazetteers to perform
attribute annotation. Machine learning approaches to NER can improve annotations of 
more complex entities and even perform entity detection without any feature
engineering. We explored many methods of Named Entity Recognition
in the context of a \gls{wde} task. First, we discuss two traditional 
approaches: Hidden Markov Models, and Linear Chain Conditional Random Fields. Then,
we discuss neural network architectures.

@@

A Markov Model is a stochastic model that computes the most probable sequence of states 
given a limited set of observable states $ S = \{s_1, s_2, ..., s_n \} $.
The Hidden Markov Model (HMM) differs from the Markov Model in that it
does not observe the states directly, but rather a probabilistic function of those 
states. For example in NER, the words are observed, however the Named Entity labels
associated with these words are not. Formally, we want to compute the most probable
sequence of labels $ Y = \{y_1, y_2, ..., y_n\} $ for a sequence of observed tokens
$ X = \{x_1, x_2, ..., x_n\} $.

\begin{equation}
Y^* = \argmax_{Y} P(Y|X)
\end{equation}

With Bayes theorem, we can write $ P(Y|X) $ as:

\begin{equation}
P(Y|X) = \frac{P(X|Y) P(Y)}{P(X)}
\end{equation}

Since $ P(X) $ is the same for all label sequences $ Y $, we can simply maximize
the probability $ P(X|Y) P(Y) $.

A HMM makes two assumptions. First, the probability of being in a given state depends 
only on a fixed number of previous states. That is:

\begin{equation}
P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k})
\end{equation}

In fact, we can get much better results on the NER task by looking at trigrams
or quadrigrams ($ k = 2 $ or $ k = 3 $) instead of bigrams as with a regular HMM. 
Some label assignments are highly improbable, such as single token named entities 
separated by a common word. These kinds of patterns can be perceived by a higher order HMM.
Second, the probability of a word depends only on its assigned label. That is:

\begin{equation}
P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i)
\end{equation}

With these assumptions, 
the probability $ P(Y|X) $ can be approximated by the expression:

\begin{equation}
P(Y|X) \propto \prod_{i=k+1}^{n} P(y_i|y_{i-1}, y_{i-2}, ..., y_{i-k}) P(x_i|y_i)
\end{equation}

All relevant probabilities can be estimated through maximum likelihood estimation from the relative
frequencies of labels and features in the corpus. The best sequence of labels can be computed 
with a variable state Viterbi approach \cite{Li2000}. However, as we increase $ k $, this computation 
becomes exponentially more expensive. The beam-search strategy may be employed for a faster 
search, but we found that for $ k \leq 4 $, the Viterbi algorithm is still viable.

@@

\subsubsection{Self-Training for Hidden Markov Models} 
\label{sssec:self_training}

As described in Section~\ref{sec:hmm}. An \gls{hmm} for the sequence labeling task 
has the form:
\begin{equation}
P(Y|X) \propto \prod_{i=1}^n P(x_i|y_i) P(y_i, y_{i-1})
\end{equation}
where $ X $ is a sequence of words and $ Y $ is a sequence of labels, both with size $ n $,
and the initial probabilities $ P(y_1|y_0) $ follow a uniform distribution across all label 
assignments.
To construct this model from the data, we need to estimate the following probabilities:
%
\begin{itemize}
  \item $ P(x_i|y_i) $: the emission probability of word $ x_i $ given label $ y_i $.
  \item $ P(y_i|y_{i-1}) $: the transition probability of going from label $ y_{i-1} $ to label $ y_i $.
\end{itemize}
%
We may consider $ x_i $ to be a binary feature vector $ x_i = \{ f_{i,1}, f_{i,2}, ..., f_{i,k} \} $
as long as all the feature distributions are independent, conditioned on $ y_i $. That is:
\begin{equation}
P(x_i|y_i) = P(f_{i,1}, f_{i,2}, ..., f_{i,k}|y_i) = \prod_{j=1}^k P(f_{i,j}|y_i)
\end{equation}
%
Also, due to the time invariance assumption, the $ P(f_{i,j}|y_i) $ probabilities 
are independent of the timestep $ i $. Therefore, for each binary feature $ f_j $ we
need only estimate the parameters $ \hat{P}(f_{j}|y) $, relative to each possible
assignment of $ y $.
The maximum likelihood estimators for these feature parameters can be obtained
from their relative frequencies, just as we did in Section~\ref{sec:hmm} for single words 
(Equation~\ref{eq:mle_words}). Then, for binary features:
%
\begin{equation}
\hat{P}(f_{j}=1|y=l) = \frac{\text{Count}(f_{j}=1, y=l)}
{\text{Count}(f_{j}=0, y=l) + \text{Count}(f_{j}=1, y=l)}
\label{eq:feature_mle}
\end{equation}
%
Where $ \text{Count}(f_{j}=1, y=l) $ is the number of times in the training set that
feature $ f_j $ was equal to one when the actual label was $ l $ (the other counts follow the same logic).
This approach yields good experimental results for textual features such as the capitalization
of a word, but if we try to use HTML structural features such as the HTML tags, we will find that
they are not very useful, contradicting our intuition.
The problem is that there is not much similarity between the HTML structure in different web pages.
For example, only because a named entity label occurs more often inside <div> tags
in a page, that does not mean this is the case for most web pages. Consider for example a faculty web page 
that shows researcher names in a table (<td> tags) in contrast to a web page that organizes researcher
names in a list (<li> tags). If there are many cases like the former page in our training set, and we use the 
HTML tag feature in a model that assigns labels to the latter page in our test set, we will probably get many 
wrong predictions.
Nonetheless, the HTML features are not useless. Inside a single web page, the HTML tag is a good predictor
of the correct labels. Words with a similar HTML context tend to have similar labels. For example, words
that happen together in a list have very similar HTML contexts and are very likely to belong to
the same category. The question is how to obtain better parameter estimators for HTML features.

Consider a set $ F^T $ of $ m $ textual features unrelated to the HTML structure:
%
\begin{equation*}
F^T = \{ f^T_1, f^T_2, ..., f^T_m \}
\end{equation*}
%
And a set $ F^H $ of $ k $ HTML features that are related to the HTML structure:
%
\begin{equation*}
F^H = \{ f^H_1, f^H_2, ..., f^H_k \}
\end{equation*}
%
Given a \gls{hmm} trained with only the first set of features $ F^T $,
we can use this model to predict the labels for an unlabeled document, and then by simply replacing
the actual labels in Equation~\ref{eq:feature_mle} with the predicted labels, we get:
%
\begin{equation}
\hat{P}(f_{j}=1|y=l) = \frac{\text{Count}(f_{j}=1, \tilde{y}=l)}
{\text{Count}(f_{j}=0, \tilde{y}=l) + \text{Count}(f_{j}=1, \tilde{y}=l)}
\end{equation}
%
\begin{equation}
\hat{P}(\text{Tag}=\text{<li>}|y=\text{I-PER}) = \frac{4}{4 + 0} = 1
\end{equation}
%
Where $ \tilde{y} $ is the label predicted by the \gls{hmm} trained with only the textual features.
We use this formulation to calculate feature probabilities for the HTML features only.
And next, we incorporate the estimators for the HTML feature probabilities in the original \gls{hmm} 
and predict the final labels with the whole set of features $ F^T \cup F^H $. 
This process could be repeated multiple times. If the predictions are becoming more accurate with
each iteration, then the estimates for the HTML feature probabilities are also likely to improve.

In a simpler explanation, the self-training strategy can be divided into the following steps:
%
\begin{itemize}
\item Train the HMM without any HTML features.
\item Compute labels for a website with the trained HMM.
\item Use the computed labels as a proxy for the actual labels in the 
website and estimate HTML feature frequencies for this website alone.
\item Recompute the labels now using the HTML feature probabilities.
\end{itemize}
%
To understand why this strategy could help labeling named entities on the web, consider the 
example shown in Figure~\ref{fig:self_training}. This example shows a snippet from a webpage 
and how a naive \gls{hmm} would probably attribute 
labels to each word. Despite being rather uncommon, North West is an actual person name,
what becomes obvious in this case once we know the HTML context where it happens 
(inside a list with other person names), but this is not so obvious if we consider the
sentence in isolation. The naive \gls{hmm} could be improved if we calculated
feature probabilities for the parent tags using proxies for the correct labels. We would find
that four times in a total of six occurrences, the correct label for a word that happened inside
a \textit{<li>} tag was \mbox{\textit{I-PER}}. By incorporating this knowledge in the model 
using the self-training strategy, we would improve the probability that words North and West 
were labeled correctly as a person name in this case.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{pics/self_training_example}
  \caption{Example of a webpage snippet with labels attributed by a HMM.}
  \label{fig:self_training}
\end{figure}

This strategy could possibly be incorporated in the Baum-Welch algorithm to provide a more 
statistically solid argument for its effectiveness, but this heuristic
already yields a consistent improvement to sequence labeling on the web. In theory, this 
strategy could be used with any sequence tagger, however retraining a classifier with new features can 
become prohibitively expensive in the case of CRFs or Neural Networks. 
In HMMs, retraining the features
is fast, because we assume feature independence and the maximum likelihood estimator can be 
obtained with a simple closed form expression.

% \subsubsection{Self training} 
% \label{sssec:self_training}
% 
% In the task of NER on HTML, there are useful features related to the HTML
% structure that can help in identifying named entities. In a given website, named
% entities tend to occur inside the same HTML tags. The HTML tag feature or other
% HTML features could easily be incorporated in the HMM. However, these 
% features are only useful inside a single website and they cannot be generalized, 
% because different websites use distinct HTML templates. 
% Therefore, we propose a self-training strategy to obtain probabilities for
% these HTML features. It is implemented like this:
% 
% \begin{itemize}
% \item Train the HMM without any HTML features.
% \item Compute labels for a website with the trained HMM.
% \item Use the computed labels as a proxy for the actual labels in the 
% website and estimate HTML feature frequencies for this website alone.
% \item Recompute the labels now using the HTML feature probabilities.
% \end{itemize}
% 
% In theory, this strategy could be used with any sequence tagger, however
% retraining a classifier with new features can become prohibitively expensive.
% This strategy is only possible because the computation of HTML feature
% frequencies can be performed very quickly. This adds very little overhead 
% to the original HMM and improves precision and recall by a considerable 
% margin.

@@

A Linear Chain Conditional Random Field (CRF) is the discriminative analog to the HMM,
it was first introduced by Lafferty \cite{Lafferty2001}. It is a distribution $ P(Y|X) $ that takes the form:

\begin{equation}
P(Y|X) = \frac{1}{Z(x)} \prod_{t=1}^{T} exp \left( \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, X) \right)
\end{equation}
\\

where $ \theta $ is the parameter vector that we are going to learn, $ f_k(y_{t-1}, y_{t}, X) $ 
are feature functions over the current timestep $ t_y $, the previous timestep $ y_{t-1}$, 
and the observation vector $ X $. And the partition function $ Z(x) $, takes the form:

\begin{equation}
Z(x) = \sum_{Y} \prod_{t=1}^{T} exp \left( \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, x) \right)
\end{equation}
\\

which is a sum over all possible label assignments $ Y $. The partition function can be efficiently
and exactly calculated with the sum-product algorithm. Parameter estimation is usually done through 
negative log likelihood minimization. The function can be optimized with techniques suitable for other 
maximum entropy models such as L-BFGS \cite{Liu1989}. The most likely label sequences can be decoded 
with the Viterbi algorithm, as was the case for HMMs.

@@

Recurrent neural networks (RNN) have been successfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feed-forward 
neural networks, RNNs can retain information in their internal state, making them more 
suitable for processing sequences, and consequently for solving text related tasks. 
Figure~\ref{fig:rnn_network} describes an RNN for sequence labeling unrolled through multiple 
timesteps.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.75\textwidth]{pics/rnn_network}
  \caption{RNN for NER}
  \label{fig:rnn_network}
\end{figure}

At each timestep, the neural network computes a hidden state $ h_t $ using an input 
vector $ x_t $ and the previous hidden state $ h_{t-1} $, that retains information from past 
iterations. Finally, the RNN produces an output vector $ y_t $ representing the label for that 
timestep. A common definition for an RNN cell is given by the equations:

\begin{flalign*}
h_t &= tanh(W_x x_t + W_h h_{t-1}) &\\
y_t &= softmax(W_y h_t) &
\end{flalign*}

Where $ W_x $, $ W_h $ and $ W_y $ are weight matrices that can be trained with the 
Backpropagation Through Time (BPTT) algorithm. Theoretically, RNNs are capable of learning
and retaining long term dependencies through their internal state $ h_t $. However, in practice,
it becomes difficult due to the vanishing gradient problem. Long short term memory networks (LSTM) were 
introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
have been popularized since then.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.75\textwidth]{pics/lstm_cell}
  \caption{LSTM Cell}
  \label{fig:lstm_cell}
\end{figure}

The equations for the LSTM cell are:

\begin{flalign*}
\Gamma_{i} &= \sigma(W_i \cdot [x_t,h_{t-1}] + b_i) &\\
\Gamma_{f} &= \sigma(W_f \cdot [x_t,h_{t-1}] + b_f) &\\ 
\Gamma_{o} &= \sigma(W_o \cdot [x_{t},h_{t-1}] + b_o) &\\
c_t        &= \Gamma_{f} \ast c_{t-1} + \Gamma_{i} \ast tanh(W_c \cdot [x_{t},h_{t-1}] + b_c) &\\
h_t        &= \Gamma_{o} \ast tanh(c_t) &
\end{flalign*}

Where $ \sigma $ is the logistic sigmoid function. $ \Gamma_i $, $ \Gamma_f $, and $ \Gamma_o $ are the input,
forget and output gates, respectively, and $ W_i $, $ W_f $, $ W_o $ are the weight 
matrices corresponding to each gate. $ c_{t} $ is the cell 
state at time $ t $ and $ h_{t} $ is the hidden state at time $ t $. 
The vector $ [x_{t},h_{t-1}] $ is formed by concatenating the current input vector 
$ x_{t} $ and the hidden vector from a previous timestep $ h_{t-1} $. Finally,
$ A \ast B $ represents the element-wise multiplication of matrices $ A $ and $ B $
and $ A \cdot B $ represents the dot product of $ A $ and $ B $.

This implementation differs from the LSTM cell described in Huang et al. \cite{Huang2015}
in that the gates $ \Gamma_i $ and $ \Gamma_f $ do not receive inputs from the previous 
cell state $ c_{t-1} $ and the output gate $ \Gamma_{o} $ does not receive inputs from the current cell 
state $ c_{t} $. This variation produces little difference in terms of model accuracy on
the performed task, but it reduces model complexity.

@@

On named entity recognition tasks, both past and future words are important 
to attribute a label at time $ t $, however a regular LSTM network only takes 
past states into consideration. A bidirectional LSTM solves this problem by stacking 
two regular LSTMs, and feeding them with observations in opposite directions. The first LSTM 
receives forward states and the second LSTM receives backward states. The hidden states from both 
networks can then be concatenated at each timestep to produce output labels. With this 
architecture, LSTM cells may use information from past and future timesteps to decide 
the label at time $ t $.

Huang et al. \cite{Huang2015} proposed a bidirectional LSTM with a CRF layer (BI-LSTM-CRF) on 
the output to tackle the sequence tagging problem. The main benefit of adding a CRF layer 
in the neural sequence model is that the labels are jointly decoded for a whole sentence 
instead of being predicted individually. Another possibility would be to use a beam search
decoder to find an optimal sequence of labels. Predicted tags should be highly correlated 
in a named entity recognition task, so it is desirable to predict sequences conjointly.
The BI-LSTM-CRF is described in Figure~\ref{fig:bi_lstm_crf}.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.75\textwidth]{pics/bi_lstm_crf}
  \caption{Bidirectional LSTM-CRF}
  \label{fig:bi_lstm_crf}
\end{figure}

@@

Ma and Hovy \cite{Ma2016} proposed to add a convolutional neural network (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
layer is described visually in Figure \ref{fig:cnn}.

\begin{figure}[h]
  \centering
	  \includegraphics[width=0.75\textwidth]{pics/cnn}
  \caption{CNN based character representations}
  \label{fig:cnn}
\end{figure}

@@

Lample et al \cite{Lample2016} proposed to use a bidirectional LSTM to model character-level 
representations on top of a BI-LSTM-CRF. Combining the forward and backward LSTM hidden states 
to form the character representation, as described in Figure~\ref{fig:lstm_char}.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.75\textwidth]{pics/lstm_char_representations}
  \caption{LSTM based character representations}
  \label{fig:lstm_char}
\end{figure}

@@

All neural models were trained using mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
parameters, considering the F1 measure in the validation set. All neural models used 
GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training.
In the case of NER on HTML, word embeddings work similarly to a gazetteer. Named entities 
with the same type have similar embeddings, so good word embeddings can achieve exceptional 
performance with little training and without a gazetteer.

@@

This chapter describes the dataset used to evaluate the performance of sequence labeling models
on the \gls{wde} task of \gls{rne}. We call it the \gls{rne} dataset.
We attested experimentally that 
models trained in a popular \gls{ner} dataset (the {CoNLL-2003} English dataset) do not perform 
well in the \gls{rne} task and this is likely due to the differences
between plain text and HTML. The lack of other \gls{ner} 
datasets built for HTML name extraction imposes the need to construct a dataset specific for \gls{rne}.

@@

This chapter is divided as follows. Section~\ref{sec:data_description} describes the 
dataset format and how it was split in
three data files. 
Section~\ref{sec:evaluation} describes how the evaluation of results in this 
dataset was carried on. 
Section~\ref{sec:dictionary} describes how we obtained a dictionary
of relevant named entities for this dataset, and discusses some baselines.
Lastly,
Section~\ref{sec:conll_comparison} compares the characteristics of the \gls{rne} dataset
with another popular \gls{ner} dataset, the {CoNLL-2003} English \gls{ner} dataset.

@@

\subsection{Features}

Thirteen categorical features were associated with each token in the dataset. They 
are presented in Table \ref{tab:features}.

>>>>

\author[João Mateus de Freitas Veneroso and Berthier Ribeiro-Neto]
       {João Mateus de Freitas Veneroso$^A$ \and
        Berthier Ribeiro-Neto$^B$\\
	Universidade Federal de Minas Gerais$^{A,B}$ \\
	Google Engineering$^A$, Belo Horizonte - MG, Brazil}

@@

Some early examples are Maximum Entropy Taggers for NER~\cite{Borthwick1998} and
\gls{pos} Tagging~\cite{Ratnaparkhi1998}. The Maximum Entropy Markov Model~\cite{McCallum2000} 
was developed just a while later, building up on the intuition of \gls{hmm}s combined with
the flexibility of discriminative approaches. However, because of the label bias problem,
this model was superseded by \gls{crf}s~\cite{Lafferty2001}. % McCallum2003
At this time, the best performing systems almost always resorted to external gazetteers 
and hand-chosen features, as is the case for the {CoNLL-2003} winning model~\cite{Florian2003}.

@@

Many \gls{wde} systems rely on hand crafted rules or gazetteers to perform
attribute annotation. Machine learning approaches to NER can improve annotations of 
more complex entities and even perform entity detection without any feature
engineering. We explored three methods of Named Entity Recognition
in the context of a \gls{wde} task. First, we discuss two traditional 
approaches: Hidden Markov Models, and Linear Chain Conditional Random Fields. Then,
we discuss neural network architectures.

@@

A Markov Model is a stochastic model that computes the most probable sequence of states 
given a limited set of observable states $ S = \{s_1, s_2, ..., s_n \} $.
The Hidden Markov Model (HMM) differs from the Markov Model in that it
does not observe the states directly, but rather a probabilistic function of those 
states. For example in NER, the words are observed, however the Named Entity labels
associated with these words are not. We want to compute the most probable
sequence of labels $ Y = \{y_1, y_2, ..., y_n\} $ for a sequence of observed tokens
$ X = \{x_1, x_2, ..., x_n\} $.
%
\begin{equation}
Y^* = \argmax_{Y} P(Y|X)
\end{equation}
%
With Bayes theorem, we can write $ P(Y|X) $ as:
%
\begin{equation}
P(Y|X) = \frac{P(X|Y) P(Y)}{P(X)}
\end{equation}
%
Since $ P(X) $ is the same for all label sequences $ Y $, we can simply maximize
the probability $ P(X|Y) P(Y) $.

A HMM makes two assumptions. First, the probability of being in a given state depends 
only on a fixed number of previous states. That is:
%
\begin{equation}
P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k})
\end{equation}
%
In fact, we can get much better results on the NER task by looking at trigrams
or quadrigrams ($ k = 2 $ or $ k = 3 $) instead of bigrams as with a regular HMM. 
Some label assignments are highly improbable, such as single token named entities 
separated by a common word. These kinds of patterns can be perceived by a higher order HMM.
Second, the probability of a word depends only on its assigned label. That is:
%
\begin{equation}
P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i)
\end{equation}
%
With these assumptions, 
the probability $ P(Y|X) $ can be calculated with the expression:
%
\begin{equation}
P(Y|X) \propto \prod_{i=k+1}^{n} P(y_i|y_{i-1}, y_{i-2}, ..., y_{i-k}) P(x_i|y_i)
\end{equation}
%
In a HMM, we need to estimate the following probabilities:
%
\begin{itemize}
  \item $ \hat{P}(x_i|y_i) $: the probability of word $ x_i $ given label $ y_i $.
  \item $ \hat{P}(y_i|y_{i-1}) $: the probability of going from label $ y_{i-1} $ to label $ y_i $.
\end{itemize}
%
These parameters can obtained with maximum likelihood estimation from the relative
frequencies of labels and words in the corpus. The best sequence of labels can be computed 
with a variable state Viterbi approach \cite{Li2000}. However, as we increase $ k $, this computation 
becomes exponentially more expensive. The beam-search strategy may be employed for a faster 
search, but we found that for $ k \leq 4 $, the Viterbi algorithm is still viable.

@@

\subsubsection{Self-Training Hidden Markov Models} 
\label{sssec:self_training}

We propose the Self-Training strategy for \gls{hmm}s to incorporate knowledge about the HTML structure
and boost the quality of the model in sequence labeling tasks for the web.
Some \gls{wde} tasks, such as researcher name extraction, need extraction systems
that can handle different webpage structures without needing to resort to human supervision
between webpages. 
The problem is that there is not a lot of similarity between the HTML structure in different web pages.
For example, only because a named entity label occurs more often inside lists in a page, we cannot
assume that this will be the case on other web pages. 
Nonetheless, the HTML structure is not useless. Inside a single web page, the HTML tag is a good predictor
of the correct labels, because words with a similar HTML context tend to have similar labels. For example, words
that happen together inside a list are very likely to belong to the same category. 
Yet, this pattern cannot be generalized to other pages, because we cannot expect that every list will
be listing the same types of entities.

The Self-Training strategy for HMMs consists of using the predicted labels as a proxy for the
correct labels and estimating HTML feature probabilities for each webpage separately.
Consider $ x_i $ to be a binary feature vector $ x_i = \{ f_{i,1}, f_{i,2}, ..., f_{i,k} \} $
where all the feature are assumed to be independent, conditioned on $ y_i $. That is:
\begin{equation}
P(x_i|y_i) = P(f_{i,1}, f_{i,2}, ..., f_{i,k}|y_i) = \prod_{j=1}^k P(f_{i,j}|y_i)
\end{equation}
%
Assuming time invariance, we need to estimate parameters $ \hat{P}(f_{j}|y) $, 
relative to each possible assignment of $ y $.
The maximum likelihood estimators for these feature parameters can be obtained
from their relative frequencies in the corpus. That is:
%
\begin{equation}
\hat{P}(f_{j}=1|y=l) = \frac{\text{Count}(f_{j}=1, y=l)}
{\text{Count}(f_{j}=0, y=l) + \text{Count}(f_{j}=1, y=l)}
\label{eq:feature_mle}
\end{equation}
%
These estimators yield good experimental results for textual features such as the 
capitalization of a word, but for the reasons already discussed, it does not work
well with HTML features, such as the current HTML tag. To make better use of the
HTML features, consider a set $ F_T $ textual features unrelated to the HTML structure
and a set $ F_H $ of HTML features related to the HTML structure.
We can use a \gls{hmm} trained exclusively with the first set of features $ F_T $
to predict the labels of an unlabeled webpage. With the predicted labels $ \tilde{y} $, we calculate
the HTML feature probabilities $ \hat{P}(f_{j}=1|\tilde{y}=l) $ using the feature counts from
that webpage alone. Next, we incorporate the estimators for the HTML feature probabilities 
in the original \gls{hmm} and predict the final labels with the whole set of features 
{$ F_T~\cup~F_H $}. This needs to be done separately for every webpage and
the process can be repeated multiple times. If the predictions are becoming more accurate with
each iteration, then the estimates for the HTML feature probabilities are also likely to improve. 
This self-training strategy showed good experimental results in the \gls{rne} task. Stated
simply, it can be divided into the following steps:
%
\begin{itemize}
\item Train the HMM without any HTML features.
\item Compute labels for a website with the trained HMM.
\item Use the computed labels as a proxy for the actual labels in the 
website and estimate HTML feature frequencies for this website alone.
\item Recompute the labels now using the HTML feature probabilities.
\end{itemize}
%
This strategy could be used with any sequence tagger, however retraining a classifier 
with new features in every webpage can become prohibitively expensive in the case of 
CRFs or Neural Networks. Contrastingly, in \gls{hmm}s, retraining the HTML features is fast, 
because we assume feature independence and the maximum likelihood estimator can be obtained 
with a simple closed form expression.

@@

A Linear Chain Conditional Random Field (CRF) is the discriminative analog to the HMM,
it was first introduced by Lafferty \cite{Lafferty2001}. The model can be described by a 
distribution $ P(Y|X) $ that takes the form:
%
\begin{equation}
P(Y|X) = \frac{1}{Z(x)} \prod_{t=1}^{T} exp \left( \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, X) \right)
\end{equation}
%
where $ \theta $ is the parameter vector that we are going to learn, $ f_k(y_{t-1}, y_{t}, X) $ 
are feature functions over the current timestep $ t_y $, the previous timestep $ y_{t-1}$, 
and the observation vector $ X $. And the partition function $ Z(x) $, takes the form:
%
\begin{equation}
Z(x) = \sum_{Y} \prod_{t=1}^{T} exp \left( \sum_{k=1}^{K} \theta_k f_k(y_{t-1}, y_t, x) \right)
\end{equation}
%
which is a sum over all possible label assignments $ Y $. The partition function can be efficiently
and exactly calculated with the sum-product algorithm. Parameter estimation is usually done through 
negative log likelihood minimization. The function can be optimized with techniques suitable for other 
maximum entropy models such as L-BFGS \cite{Liu1989}. The most likely label sequences can be decoded 
with the Viterbi algorithm.

@@

Recurrent neural networks (RNN) have been successfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feed-forward 
neural networks, RNNs can retain information in their internal state, making them more 
suitable for processing sequences, and consequently for solving text related tasks. 
Figure~\ref{fig:rnn_network} describes an RNN for sequence labeling unrolled through multiple 
timesteps. 
%
\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{pics/rnn_network}
  \caption{RNN for NER}
  \label{fig:rnn_network}
\end{figure}
%
At each timestep, the neural network computes a hidden state $ h_t $ using an input 
vector $ x_t $ and the previous hidden state $ h_{t-1} $, that retains information from past 
iterations. Finally, the RNN produces an output vector $ y_t $ representing the label for that 
timestep. A common definition for an RNN cell is given by the equations:
%
\begin{align*}
h_t &= tanh(W_x x_t + W_h h_{t-1}) &\\
y_t &= softmax(W_y h_t) &
\end{align*}
%
Where $ W_x $, $ W_h $ and $ W_y $ are weight matrices that can be trained with the 
Backpropagation Through Time (BPTT) algorithm. Theoretically, RNNs are capable of learning
and retaining long term dependencies through their internal state $ h_t $. However, in practice,
it becomes difficult due to the vanishing gradient problem. Long short term memory networks (LSTM) were 
introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
have been popularized since then.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{pics/lstm_cell}
  \caption{LSTM Cell}
  \label{fig:lstm_cell}
\end{figure}

The equations for the LSTM cell are:
%
\begin{align*}
\Gamma_{i} &= \sigma(W_i \cdot [x_t,h_{t-1}] + b_i) &\\
\Gamma_{f} &= \sigma(W_f \cdot [x_t,h_{t-1}] + b_f) &\\ 
\Gamma_{o} &= \sigma(W_o \cdot [x_{t},h_{t-1}] + b_o) &\\
c_t        &= \Gamma_{f} \ast c_{t-1} + \Gamma_{i} \ast tanh(W_c \cdot [x_{t},h_{t-1}] + b_c) &\\
h_t        &= \Gamma_{o} \ast tanh(c_t) &
\end{align*}
%
Where $ \sigma $ is the logistic sigmoid function. $ \Gamma_i $, $ \Gamma_f $, and $ \Gamma_o $ are the input,
forget and output gates, respectively, and $ W_i $, $ W_f $, $ W_o $ are the weight 
matrices corresponding to each gate. $ c_{t} $ is the cell 
state at time $ t $ and $ h_{t} $ is the hidden state at time $ t $. 
The vector $ [x_{t},h_{t-1}] $ is formed by concatenating the current input vector 
$ x_{t} $ and the hidden vector from a previous timestep $ h_{t-1} $. Finally,
$ A \ast B $ represents the element-wise multiplication of matrices $ A $ and $ B $
and $ A \cdot B $ represents the dot product of $ A $ and $ B $.

This implementation differs from the LSTM cell described in Huang et al. \shortcite{Huang2015}
in that the gates $ \Gamma_i $ and $ \Gamma_f $ do not receive inputs from the previous 
cell state $ c_{t-1} $ and the output gate $ \Gamma_{o} $ does not receive inputs from the current cell 
state $ c_{t} $. This variation produces little difference in terms of model accuracy on
the performed task, but it reduces model complexity.

@@

On \gls{ner} tasks, both past and future words are important 
to attribute a label at time $ t $, however a regular LSTM network only takes 
past states into consideration. A bidirectional LSTM solves this problem by stacking 
two regular LSTMs, and feeding them with observations in opposite directions. The first LSTM 
receives forward states and the second LSTM receives backward states. The hidden states from both 
networks can then be concatenated at each timestep to produce output labels. With this 
architecture, LSTM cells may use information from past and future timesteps to decide 
the label at time $ t $.

Huang et al. \shortcite{Huang2015} proposed a bidirectional LSTM with a CRF layer (BI-LSTM-CRF) on 
the output to tackle the sequence tagging problem. The main benefit of adding a CRF layer 
in the neural sequence model is that the labels are jointly decoded for a whole sentence 
instead of being predicted individually. Another possibility would be to use a beam search
decoder to find an optimal sequence of labels. Predicted tags should be highly correlated 
in a named entity recognition task, so it is desirable to predict sequences conjointly.
The BI-LSTM-CRF is described in Figure~\ref{fig:bi_lstm_crf}.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{pics/bi_lstm_crf}
  \caption{Bidirectional LSTM-CRF}
  \label{fig:bi_lstm_crf}
\end{figure}

@@

Ma and Hovy \shortcite{Ma2016} proposed to add a convolutional neural network (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information. The CNN
layer is described visually in Figure \ref{fig:cnn}.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{pics/cnn}
  \caption{CNN based character representations}
  \label{fig:cnn}
\end{figure}

@@

Lample et al \shortcite{Lample2016} proposed to use a bidirectional LSTM to model character-level 
representations on top of a BI-LSTM-CRF. Combining the forward and backward LSTM hidden states 
to form the character representation, as described in Figure~\ref{fig:lstm_char}.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.5\textwidth]{pics/lstm_char_representations}
  \caption{LSTM based character representations}
  \label{fig:lstm_char}
\end{figure}

@@

In the experiments, all neural models were trained using mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
parameters, considering the F1 measure in the validation set. All neural models used 
GloVe 300-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training.

@@

This section describes the dataset used to evaluate the performance of sequence labeling models
on the \gls{wde} task of \gls{rne}. We call it the \gls{rne} dataset.
We attested experimentally that 
models trained in a popular \gls{ner} dataset (the {CoNLL-2003} English dataset) do not perform 
well in the \gls{rne} task and this is likely due to the differences
between plain text and HTML. The lack of other \gls{ner} 
datasets built for HTML name extraction imposes the need to construct a dataset specific for \gls{rne}.

@@

@@
